# Results

## Regression coefficients for all methods
First, we look at the beta's generated from each method.

Because each model we fit uses a different method. The beta coefficients are different for each model. The table belows showcases the difference

#### TABLE OF COEFFICIENTS HERE
```{r kable, echo=FALSE}
coefs_df <- data.frame('OLS' = ols_coef,
                       'Ridge' = best_ridge_coef,
                       'Lasso' = best_lasso_coef,
                       'PCR' = best_pcr_coef,
                       'PLSR' = plsr_coef)
table(coefs_df)
```
####

The effect on the variable `Balance` from each variable with negative coefficient varies for each model. 

In OLS, Lasso, Ridge and PLSR, `Income` has the biggest effect on variabe `Balance`.   

Across the models, `Student:Female` and `Married:Yes` have similar effect on variable `Balance`.

### Official coefficients for different models

we will plot the official coefficients to have a better understanding of how coefficient values differ across models.

###LINE CHART
``` {r, echo = FALSE}
par(mar=c(7, 5, 2, 2))

matplot(coefs_df, type = "l", xaxt = "n", ylab = "Coefficient Estimate", col = c(1:5))

axis(1, at = 1:9, labels = row.names(coefs_df), cex.axis = 0.7, las = 2)
legend("topright", inset=.05, legend=c("OLS", "Lasso", "Ridge", "PCR", "PLSR"), pch=1, col=c(1:5), horiz=FALSE, bty = "n")
title("Official Coefficients")
```
###

As shown in the chart,  coefficients of PCR fluctuate the least and differ from the coefficients yielded by the other models. 

### Comparing MSE values 
We want to find out which regression technique best predicts 
values of `Balance`, 

we compare the MSE of the various models.

### TAble of MSE for each regression  technique
```{r, echo=FALSE}
kable(mse_df)
```

###

As shown in the table, we see that  Ridge regression yields minimum MSE.  Ridge regression thererfore model predicts `Balance` within the smallest range of all of our tested models. Because the Ridge regression has the minimum MSE, we conclude that Ridge yield best predictions for `Balance`.



